Install packages
```{r}
#install.packages('mixtools')
#install.packages('mclust')

library('mixtools')
library('mclust')
library('dplyr')


library(ggplot2)
library(gridExtra)
library(stringr)
library(tidyverse)
```


Pull data
```{r}
#Load data
merged = read.csv('merged.csv',header=TRUE)

# General psychopathology scores for all participants
X = merged$GENERALB  
```



GMM (2 cluster solution determined by Python script)
```{r}
gmm <- function(X,modelNames) {

  # Params
  # X : observations
  # Returns:
  # results : list
  
  N <- length(X)

  model <- Mclust(X, G=2, modelNames) #G = two clusters
  
  means <- model$parameters$mean

  vars <- model$parameters$variance$sigmasq

  pros <- model$parameters$pro

  m1 <- means[1]

  m2 <- means[2]

  #V = Unequal variance assumed between groups
  #E = Equal variance assumed between groups
  
  if (modelNames == 'V') {
    v1 <- vars[1]
    v2 <- vars[2]
  } else if (modelNames == 'E') {
    v1 <- vars
    v2 <- vars
  } else (
    stop('Only prepared to handle "E" or "V" for `variance`')
  )

  p1 <- pros[1]

  p2 <- pros[2]

  g1 <- function(x) dnorm(x, m=m1, sd=sqrt(v1)) * p1

  g2 <- function(x) dnorm(x, m=m2, sd=sqrt(v2)) * p2

  g.diff <- function(x) g2(x) - g1(x)

  intersection = NA

  gmm.membership = rep(NA, N)

  tryCatch(

    expr = {

      root <- uniroot(g.diff, interval=c(m1-(2*sqrt(v1)), m2+(2*sqrt(v2))))

      intersection <- root$root

      gmm.membership <- ifelse(model$classification == 2, 1, 0)

    },

    error = function(e) {

      print("Failure finding root!")

    }

  )

 

  results = list(

    "intersection" = intersection,

    "gmm.membership" = gmm.membership,

    "model" = model,

    "g1" = g1,

    "g2" = g2

  )
 
  return(results)

}
```

Run GMM on psychopathology data 
```{r}
results<-gmm(X, 'V')

```



```{r}

#pull membership assignments and merge with original dataframe
membership= as.data.frame(results$gmm.membership)
colnames(membership)[colnames(membership) == 'results$gmm.membership'] <- 'membership'
df_membership = cbind(merged,membership)

#Check group assignments
table(df_membership$membership) # 0 = 3980 1= 5047
mean(subset(df_membership$GENERALB, df_membership$membership == -1)) #-0.695753
mean(subset(df_membership$GENERALB, df_membership$membership == 1))  #.6583131

#Reassign controls as -1 as per hydra methodology
df_membership$membership[df_membership$membership == 0] <- -1

#Write to csv 
#write.csv(df_membership, file="~/Desktop/HYDRA/HYDRAMembership.csv", row.names=F, quote=F)

```


Covariates: Create a covariates dataset with subject IDs, age, and sex
```{r}

df_AgeSex <- df_membership[c(grep("subnum_char_b|age_b|FEMALE_b",names(df_membership)))]
df_AgeSex <- df_AgeSex[order(df_AgeSex$subnum_char_b),]

```


Brain Features: Create a features dataset with subject ID, cortical thickness and gray matter volume 
```{r}
#volume 
df_vol <- df_membership[c(grep("subnum_char_b|smri_vol_cdk_|smri_vol_scs_",names(df_membership)))]
df_vol = subset(df_vol, select = -c(smri_vol_cdk_total_b) )

#thickness
df_ct <- df_membership[c(grep("subnum_char_b|smri_thick_cdk_|membership",names(df_membership)))]

#CT and volume JLF
df_ctVol <- merge(df_vol,df_ct,by="subnum_char_b", all = TRUE)

#Put ids in ascending order 
df_ctVol <- df_ctVol[order(df_ctVol$subnum_char_b),]


```



Check Files - it is very important to make sure the subject numbers are aligned for the features dataset and the covariates dataset. 
```{r}


##The covariates and features files MUST have subjects in the same order. Check that this true (correlation between ids should = 1)
df_corr_ctVol <- cor(df_AgeSex$subnum_char_b,df_ctVol$subnum_char_b) # = 1.00


##Check that the variables are in the correct order with the correct n
nrow(df_AgeSex)
nrow(df_ctVol)

```



Save Files
```{r}

#Save covariates files to use with HYDRA
write.csv(df_AgeSex, file="~/Desktop/HYDRA/df_AgeSex_GMM.csv", row.names=F, quote=F)

#Save brain features to use with HYDRA
write.csv(df_ctVol, file="~/Desktop/HYDRA/df_ctVol_GMM.csv", row.names=F, quote=F)
```

